Tables

### 2019-12-23 manuscript/tables.Rmd

PDI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

>>>>

PDI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results for oak decline severity cases in the PDI index model. Top four important descriptors show. Descriptors ordered by descending absolute weight within each case.') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results of oak decline type and severity in the DAI index model. Top four important descriptors shown. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(5,width = '4cm') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```
